Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
updated rl section

\subsection{Reinforcement learning}
We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL when used in conjuction with an
uncertainty-guided exploration strategy.
Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
hope to discover new high reward actions (exploration)?

Prior work has used GP dynamic models \cite{deisenrothPILCO2011,kamtheDataEfficient2018}, ensembles of neural
networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
variational inference \cite{galImproving2016,houthooftVIME2017}

@@

% A key challenge in RL is balancing the trade-off between exploration and exploitation.
% That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
% hope to discover new actions which lead to high reward (exploration)?
% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
% demonstrating the quality of our uncertainty estimates.
% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem and more details of our experiments.

@@

by using it to learn a dynamics model and
evaluate the
We test \our by using it to learn a dynamics model
our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
The goal is to swing the pole up and balance it around the upward position.
We increase the  difficulty of exploration in this environment by using a sparse reward function.

We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
% See \cref{app:rl} for more details of our experiments.
We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
% As expected DDPG is the least sample inefficient
The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.

>>>>

\subsection{Reinforcement learning}
% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
% Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
% Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
% hope to discover new high reward actions (exploration)?

% when used in conjuction with an
% uncertainty-guided exploration strategy.

@@

A key challenge in RL is balancing the trade-off between exploration and exploitation.
That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
select new ones in hope to discover actions leading to higher reward (exploration).
One promising direction is to model the uncertainty associated with a learned transition dynamics and use it to guide exploration.
Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
and variational inference \cite{galImproving2016,houthooftVIME2017}.
There are then many ways to leverage uncertainty in model-based RL, for example,
taking an expectation over epistemic uncertainty  \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
sampling from the posterior, akin to Thompson sampling but referred to as posterior sampling RL
\cite{osbandMoreEfficientReinforcement2013},
and methods based on upper confidence bounds (UCB) \cite{curiEfficient2020}.

% Uncertainty-guided decision making strategies
We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem and more details of our experiments.

We test \our by using it to learn a dynamics model
our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
The goal is to swing the pole up and balance it around the upward position.
We increase the  difficulty of exploration in this environment by using a sparse reward function.

We compare \our (cyan) to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
% See \cref{app:rl} for more details of our experiments.
We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
% As expected DDPG is the least sample inefficient
The training curves in \cref{fig:rl} show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.

% \cite{deisenrothPILCO2011},
% Posterior sampling

% based on

% Model-based RL algorithims are more sample efficient than their model-free counterparts as they learn a model of the transition dynamics and
% use it to augment the RL loop.

% Prior work has used show that modelling uncertainty in the transition dynamics can further improve exploration and thus sample efficiency.
% For example, with GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
% and variational inference \cite{galImproving2016,houthooftVIME2017}

% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.

% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
% demonstrating the quality of our uncertainty estimates.
% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.

@@

% by using it to learn a dynamics model and
% evaluate the
% We test \our by using it to learn a dynamics model
% our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
% The goal is to swing the pole up and balance it around the upward position.
% We increase the  difficulty of exploration in this environment by using a sparse reward function.

% We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
% To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
% % See \cref{app:rl} for more details of our experiments.
% We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
% % As expected DDPG is the least sample inefficient
% The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.
